---
title: 'Practical Mixed Models for Actuaries'
subtitle: 'Code Chuncks Extracted via AWK script'
author: 'Ernesto Schirmacher'
output: html_notebook
temporary: in review (to be deleted)
---

## Chapter 3--Credibility

```{r}
#| include: true
#| message: false

library(tidyverse)
library(patchwork)
library(kableExtra)
library(GLMsData)
library(statmod)
library(actuar)
library(lme4)
```

```{r}
#| include: true

source("buehlmann-gisler-calculations.R")
```

```{r}
margin <- c(0.01, 0.05, 0.1)
probs <- c(0.9, 0.95, 0.975, 0.99)
cv <- c(0.00, 0.10, 0.40)
```

```{r}
dnm <- list(paste(probs * 100, "%", sep = ""), 
            paste(margin * 100, "%", sep = ""))
alpha <- 1 - probs
qs <- qnorm(1 - alpha/2, mean = 0, sd = 1)
tb <- outer(qs, margin, function(x,y) {(x/y)^2})
tb1 <- tb * (1 + cv[1]^2)
tb2 <- tb * (1 + cv[2]^2)
tb3 <- tb * (1 + cv[3]^2)
dimnames(tb1) <- dnm
dimnames(tb2) <- dnm
dimnames(tb3) <- dnm
```

```{r}
round(tb1,0)
```

```{r}
round(tb2, 0)
```

```{r}
round(tb3, 0)
```

```{r}
#| include: false

rm(margin, probs, cv, dnm, alpha, qs, tb, tb1, tb2, tb3)
```

```{r}
#| echo: true
#| label: fig-limited-fluctuation-credibility-factors
#| fig-cap: "Limited fluctuation credibility factors. The coefficient of variation is 10% with a margin of 5% and a probability equal to 90%. Full credibility is reached with 1,093 expected claims. Note that if a portfolio has 250 expected claims, then it would have a credibility factor of almost 50%.  A credibility factor of 75% requires about 625 claims."

fc <- (1.645/0.05)^2 * (1 + 0.1^2)
x <- seq(0, 1300)
y <- pmin(sqrt(x / fc), 1)
p <- ggplot(data = tibble(x = x, y = y),
            mapping = aes(x = x, y = y)) +
  geom_line() +
  labs(x = "Expected Number of Claims",
       y = "Credibility Factor (Z)")
p <- p + geom_point(data = tibble(x = 1093.23, y = 0),
                    mapping = aes(x = x, y = y),
                    color = "red")
p <- p + annotate(geom = "text",
                  x = 1093.23,
                  y = 0.25,
                  label = "Full\nCredibility",
                  color = "red")
p <- p + geom_segment(data = tibble(x = 1093.23,
                                    y = 0.17,
                                    xend = 1093.23,
                                    yend = 0.02),
                      aes(x = x, y = y,
                          xend = xend, yend = yend),
                          arrow = arrow(length = unit(0.03, "npc")),
                          color = "red")
p <- p + geom_segment(data = tibble(x = 1093.23,
                                    y = 0.32,
                                    xend = 1093.23,
                                    yend = 0.98),
                      aes(x = x, y = y,
                          xend = xend, yend = yend),
                          arrow = arrow(length = unit(0.03, "npc")),
                          color = "red")
p
rm(fc, x, y, p)
```

```{r}
#| echo: true

dta <- tibble(class = factor(rep(1:3, each = 4),
                             levels = 1:3),
              time = rep(1:4, times = 3),
              value = c(625, 675, 600, 700,
                        750, 800, 650, 800,
                        900, 700, 850, 950))
```

```{r}
#| include: true

dtb <- pivot_wider(dta,
                   names_from = time,
                   values_from = value)
```

```{r}
#| echo: true
#| label: tbl-balanced-example
#| tbl-cap: "Claims experience for a portfolio of three risk classes that have been observed over four calendar years."

kbl(dtb,
    col.names = c("Class", "1", "2", "3", "4"),
    align = "ccccc",
    booktabs = TRUE) %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" " = 1, "Time" = 4))
```

```{r}
#| echo: true
#| label: fig-balanced-example
#| fig-cap: "Claims experience for a portfolio of three risk classes that have been observed over four years.  What should the estimate, for each risk class, be in year five?"

ggplot(data = dta,
       mapping = aes(x = time,
                     y = value,
                     group = class,
                     pch = class)) +
  geom_line(color = "gray") +
  geom_point(size = 2) +
  xlim(1,5) +
  annotate("text",
           x = rep(5,3),
           y = c(834.375, 750, 665.625),
           label = rep("?", 3)) +
  labs(x = "Observation Year",
       y = "Claims Experience")
```

```{r}
J <- length(levels(dta$class))
Tm <- length(unique(dta$time))
X_jt <- dta$value

X.bar <- mean(X_jt)
Xj.bar <- tapply(X_jt, dta$class, mean)
SSB <- Tm * sum((Xj.bar - X.bar)^2)
MSB <- SSB/(J - 1)
```

```{r}
SSW <- sum((X_jt - rep(Xj.bar, each = Tm))^2)
MSW <- SSW / (J * (Tm - 1))
```

```{r}
c("SSB" = SSB, "MSB" = MSB, "SSW" = SSW, "MSW" = MSW)
```

```{r}
round(c("F.stat" =  MSB / MSW,
"5% Cr.Vl" = qf(0.95, J - 1, J * (Tm - 1)),
"p-value" = pf(MSB/MSW, J - 1, J * (Tm - 1),
               lower.tail = FALSE)), 4)
```

```{r}
fm <- lm(value ~ class, data = dta)
anova(fm)
```

```{r}
dta$value[dta$class == 3]
```

```{r}
f <- function(m, c.value, dt, cls) {
  idx <- dt$class == cls
  dt$value[idx] <- dt$value[idx] - m
  fm <- lm(value ~ class, data = dt)
  f.val <- anova(fm)[1,4]
  ans <- (f.val - c.value)^2
  return(ans)
}
```

```{r}
optimize(f, c(0, 100),
         c.value = qf(0.95, 2, 9), 
         dt = dta, 
         cls = 3)
```

```{r}
#| include: false

rm(dt, dtb, fm, J, m, Tm, SSB, MSB, SSW, MSW,
   X_jt, X.bar, Xj.bar, idx, f)
```

```{r}
J <- length(levels(dta$class))
Tm <- length(unique(dta$time))
cls <- dta$class

o <- order(dta$class, dta$time)
Xjt <- dta$value[o]
```

```{r}
X.bar <- mean(Xjt)
Xj.bar <- tapply(Xjt, cls, mean)
```

```{r}
sigmaj.sq <- tapply(
  (Xjt - rep(Xj.bar, each = Tm))^2, cls, sum) / (Tm - 1)
sigma.sq <- mean(sigmaj.sq)
```

```{r}
Var.Xj.bar <- sum((Xj.bar - X.bar)^2) / (J - 1)
```

```{r}
tau.sq <- Var.Xj.bar - sigma.sq / Tm
```

```{r}
Z <- Tm / (Tm + sigma.sq / tau.sq)
Z * Xj.bar + (1 - Z) * X.bar
```
Adding these forecasts to our earlier graph gives us
@fig-balanced-example-next-year.

```{r}
#| echo: true
#| label: fig-balanced-example-next-year
#| fig-cap: "Claims experience for a portfolio of three risk classes that have been observed over four years.  The credibility weighted estimate for the next year is shown"

tb <- tibble(class = factor(c(1,2,3,1,2,3)),
             time = c(4, 4, 4, 5, 5, 5),
             value = c(700, 800, 950, 665.625, 750, 834.375))
ggplot(data = dta,
       mapping = aes(x = time,
                     y = value,
                     group = class,
                     pch = class)) +
  geom_line(color = "gray") +
  geom_line(data = tb,
            mapping = aes(x = time,
                          y = value,
                          group = class),
            color = "red") +
  geom_point() +
  geom_point(data = subset(tb, time == 5),
             mapping = aes(x = time,
                           y = value),
             color = "red") +
  xlim(1,5) +
  annotate("text",
           x = rep(5,3),
           y = c(834.375, 750, 665.625),
           label = rep("?", 3)) +
  labs(x = "Observation Year",
       y = "Claims Experience")
```

```{r}
#| include: true

dtb <- pivot_wider(dta,
                   names_from = time,
                   values_from = value)
dtb
```

```{r}
BB <- cm( ~ class,
          data = dtb,
          ratios = 2:5)
summary(BB)
```

```{r}
#| echo: true

rm(cls, J, o, sigma.sq, sigmaj.sq, tau.sq, Tm,
   Var.Xj.bar, X.bar, Xj.bar, Xjt, Z, tb, BB, dtb)
```

```{r}
J <- 100; Tm <- 5
j <- as.factor(rep(1:J, each = Tm))

m <- 80
t2 <- 64
s2 <- 100
```

```{r}
set.seed(12094851)
w.jt <- 0.5 + runif(J * Tm)
X.jt <- m + rep(rnorm(J, 0, sqrt(t2)), each = Tm) +
            rnorm(J * Tm, 0, sqrt(s2/w.jt))
```

```{r}
#| echo: true

dta <- tibble(risk = j,
              X.jt = X.jt,
              W.jt = w.jt)
write_csv(dta, "BS-simulated-data.csv")
rm(dta)
```

```{r}
(av <- anova(lm(X.jt ~ j, weights = w.jt)))
```

```{r}
(s2.hat <- av[2,3])
```

```{r}
(m.hat <- X.bb <- sum(w.jt * X.jt) / sum(w.jt))
```

```{r}
w.jc <- tapply(w.jt, j, sum)
w.cc <- sum(w.jc)
X.jb <- tapply(w.jt * X.jt / w.jc[j], j, sum)
```

```{r}
num <- sum(w.jc * (X.jb - X.bb)^2) - (J - 1) * s2.hat
den <- w.cc - sum(w.jc^2 / w.cc)
(t2.hat <- num / den)
```

```{r}
Zj.hat <- w.jc / (w.jc + s2.hat / t2.hat)
```

```{r}
(X.z <- sum(Zj.hat * X.jb) / sum(Zj.hat))
```

```{r}
P.hat <- Zj.hat * X.jb + (1 - Zj.hat) * X.z
```

```{r}
P.hat[1:20]
```

```{r}
#| include: false

rm(av, den, j, m, num, s2, t2, w.cc, w.jc,
   X.bb, X.jb)
```

```{r}
D <- cbind(risk.class = 1:J, 
           as.data.frame(matrix(X.jt, 
                                nrow = J, 
                                ncol = Tm, 
                                byrow = TRUE)),
           as.data.frame(matrix(w.jt, 
                                nrow = J, 
                                ncol = Tm, 
                                byrow = TRUE)))
```

```{r}
(BS <- cm(~ risk.class, 
          data = D, 
          ratios = 2:6, 
          weights = 7:11))
```
For the first 5 risk classes, our by-hand calculations
match those from the `cm()` function.

```{r}
rbind("   cm():" = predict(BS)[1:5],
      "by-hand:" = P.hat[1:5])
```

```{r}
all(round(abs(predict(BS) - P.hat), 10) == 0)
```

```{r}
#| include: false

rm(BS, D, J, m.hat, P.hat, s2.hat, t2.hat, Tm, w.jt,
   X.jt, X.z, Zj.hat)
```

```{r}
#| include: true

data("hachemeister", package = "actuar")
dta <- hachemeister
rm(hachemeister)
```

```{r}
#| echo: true
#| label: tbl-hachemeister-data
#| tbl-cap: "The Hachemeister data. Number of claims and severity for five different states from private passenger automobile insurance (bodily injury coverage)."

time <- c("3Q'70", "4Q'70",
          paste(1:4, "Q'71", sep = ""),
          paste(1:4, "Q'72", sep = ""),
          "1Q'73", "2Q'73")
tb <- cbind(time, as.data.frame(t(dta[,2:13])),
            as.data.frame(t(dta[,14:25])))
kbl(tb,
    digits = 0,
    row.names = FALSE,
    col.names = c("Period", rep(1:5, 2)),
    align = "lrrrrrrrrrr",
    format.args = list(big.mark = ','),
    booktabs = TRUE) %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" ", "Claim Severity by State" = 5,
                     "Number of Claims by State" = 5))

rm(time, tb)
```

```{r}
#| echo: true

db.1 <- pivot_longer(as.data.frame(dta[,1:13]),
                     cols = 2:13,
                     names_to = "time",
                     names_prefix = "ratio.",
                     values_to = "severity")
db.2<- pivot_longer(as.data.frame(dta[,c(1,14:25)]),
                    cols = 2:13,
                    names_to = "time",
                    names_prefix = "weight.",
                    values_to = "claims")
db <- inner_join(db.1, db.2, by = c("state", "time"))
db$state <- as.character(db$state)
db$time <- as.numeric(db$time)
write_csv(db, "hachemeister-data.csv")
rm(db.1, db.2)
```

```{r}
#| echo: true
#| label: fig-hachemeister-data
#| fig-cap: "Hachemeister data showing quarterly experience for private passenger auto (bodily injury coverage) severity for five different states from the third quarter of 1970 to the second quarter of 1973 (12 observations). The observations for each state have been connected with light gray lines to emphasize the state individual trends.  State 4 has been highlighted with thicker line segments."

A <- filter(db, state %in% c(1:3,5))
B <- filter(db, state %in% 4)
C <- cbind(state = "ALL",
           summarize(group_by(db, time),
                     clms = sum(claims),
                     loss = sum(claims * severity),
                     sev = loss / clms))
p <- ggplot(data = A,
       mapping = aes(x = time,
                     y = severity,
                     group = state)) +
  geom_line(color = "gray") +
  geom_point(color = "gray") +
  labs(x = "Time",
       y = "Severity") +
  scale_x_continuous(breaks = 1:12,
                     labels = c(paste(3:4, "Q'70", sep = ""), 
                                paste(1:4, "Q'71", sep = ""), 
                                paste(1:4, "Q'72", sep = ""),
                                paste(1:2, "Q'73", sep = "")),
                     minor_breaks = NULL)
p <- p + geom_line(data = B,
                   mapping = aes(x = time,
                                 y = severity),
                   col = "gray", linewidth = 1.25) +
  geom_point(data = B,
            mapping = aes(x = time,
                          y = severity),
            color = "darkgray") +
  annotate("text",
           x = rep(12.3, 5),
           y = db$severity[db$time == 12],
           label = paste("State", 1:5, sep = " "),
           size = 3)
p
```

```{r}
#| echo: true
#| message: false
#| label: fig-hachemeister-individual-trends
#| fig-cap: "Hachemeister data including individual regression lines for each state (shown in light purple) and a 'countrywide' regression line (shown in red) for the combined data of all five states."

q <- p + geom_smooth(data = A,
                     method = "lm",
                     mapping = aes(x = time,
                                   y = severity,
                                   weight = claims),
                     se = FALSE,
                     color = "#f1b6da",
                     linewidth = 0.5) +
  geom_smooth(data = B,
              method = "lm",
              mapping = aes(x = time,
                            y = severity,
                            weight = claims),
              se = FALSE,
              color = "#f1b6da",
              linewidth = 0.5) +
  geom_smooth(data = C,
              method = "lm",
              mapping = aes(x = time,
                            y = sev,
                            weight = clms),
              se = FALSE,
              color = "red",
              linewidth = 0.5)
q
rm(A, B, C, p, q)
```

```{r}
W.jt <- db$claims
T.jt <- db$time
X.jt <- db$severity
S <- db$state
N <- length(unique(T.jt))
J <- length(unique(S))
```

```{r}
W.jb <- tapply(W.jt, S, sum)
W.bb <- sum(W.jb)
Ej.t <- tapply(W.jt * T.jt, S, sum) / W.jb
Ej.t2 <- tapply(W.jt * T.jt^2, S, sum) / W.jb
Ej.X <- tapply(W.jt * X.jt, S, sum) / W.jb
Ej.tX <- tapply(W.jt * T.jt * X.jt, S, sum) / W.jb
Vj.t <- Ej.t2 - Ej.t^2
Ws.jb <- Vj.t * W.jb
Ws.bb <- sum(Ws.jb)
```

```{r}
Bj <- rbind((Ej.t2 * Ej.X - Ej.t * Ej.tX) / Vj.t,
            (Ej.tX - Ej.t * Ej.X) / Vj.t)
dimnames(Bj) <- list(c("Intercept", "Slope"),
                     1:5)
round(Bj, 2)
```

```{r}
lm.st4 <- lm(severity ~ time,
             data = db,
             subset = state == 4,
             weights = claims)
coef(lm.st4)
```

```{r}
Ys <- cbind(rep(1, 12), 1:12)
mu.jt <- as.vector(Ys %*% Bj)
sigmaj.sq <- tapply(W.jt * (X.jt - mu.jt)^2, S, sum) / (N - 2)

rm(Ys, mu.jt)
```

```{r}
sigma.sq <- mean(sigmaj.sq)
```

```{r}
B0.bar <- sum(W.jb / W.bb * Bj[1,])
```

```{r}
term.1 <- (J - 1) / J
term.2 <- W.jb / W.bb
term.3 <- 1 - term.2
term.4 <- sum(term.2 * term.3)
c0 <- term.1 / term.4

rm(term.1, term.2, term.3, term.4)
```

```{r}
term.1 <- J / (J - 1)
term.2 <- W.jb / W.bb
term.3 <- (Bj[1,] - B0.bar)^2
term.4 <- J * sigma.sq / W.bb
tau0.sq <- c0 * (term.1 * sum(term.2 * term.3) - term.4)

rm(term.1, term.2, term.3, term.4)
```

```{r}
B1.bar <- sum(Ws.jb / Ws.bb * Bj[2,])
```

```{r}
term.1 <- (J - 1) / J
term.2 <- Ws.jb / Ws.bb
term.3 <- 1 - term.2
term.4 <- sum(term.2 * term.3)
c1 <- term.1 / term.4

rm(term.1, term.2, term.3, term.4)
```

```{r}
term.1 <- J / (J - 1)
term.2 <- Ws.jb / Ws.bb
term.3 <- (Bj[2,] - B1.bar)^2
term.4 <- J * sigma.sq / Ws.bb
tau1.sq <- c1 * (term.1 * sum(term.2 * term.3) - term.4)

rm(term.1, term.2, term.3, term.4)
```

```{r}
k0 <- sigma.sq / tau0.sq
k1 <- sigma.sq / tau1.sq

Determ <- (W.jb + k0) * (W.jb * Ej.t2 + k1) - (W.jb * Ej.t)^2
term.11 <- W.jb * Vj.t + k1
term.12 <- k1 * Ej.t
term.21 <- k0 * Ej.t
term.22 <- W.jb * Vj.t + k0 * Ej.t2

#rm(k0, k1)
```

```{r}
A <- function(j) {
  M <- matrix(c(term.11[j], term.12[j],
                term.21[j], term.22[j]),
              nrow = 2, ncol = 2, byrow = TRUE)
  ans <- W.jb[j] / Determ[j] * M
  dimnames(ans) <- list(c("", ""),
                        c("", ""))
  return(ans)
}
```

```{r}
B.gls <- solve(A(1) + A(2) + A(3) + A(4) + A(5)) %*% 
  (A(1) %*% Bj[,1] + A(2) %*% Bj[,2] + A(3) %*% Bj[,3] +
     A(4) %*% Bj[,4] + A(5) %*% Bj[,5])
```

```{r}
CW <- function(j){
  I <- diag(1, nrow = 2, ncol = 2)
  ans <- A(j) %*% Bj[,j] + (I - A(j)) %*% B.gls
  dimnames(ans) <- list(c("Intercept", "Slope"),
                        paste("State", j, sep = " "))
  return(ans)
}
```

```{r}
round(A(1), 4)
```
and the credibility weighted estimate of the intercept 
and slope for state 1 are 

```{r}
round(CW(1), 2)
```

```{r}
CM <- rbind(A(1), A(2), A(3), A(4), A(5))
dimnames(CM) <- list(rep(1:5, each = 2),
                     c("Credibility", "Matrix"))
BM <- rbind(Bj[1,1], Bj[2,1],
            Bj[1,2], Bj[2,2],
            Bj[1,3], Bj[2,3], 
            Bj[1,4], Bj[2,4], 
            Bj[1,5], Bj[2,5])
CR <- rbind(CW(1), CW(2), CW(3), CW(4), CW(5))
BG <- rbind(B.gls,B.gls,B.gls,B.gls,B.gls)
ST <- cbind(CM, BM, CR, BG)
dimnames(ST) <- list(rep(1:5, each = 2),
                     c("Credibility", "Matrix",
                       "Standalone", "Credibility", "Collective"))
round(ST, 4)

rm(CM, BM, CR, BG)
```

```{r}
#| echo: true

db2 <- db
db2$SA <- NA   # Stand-alone prediction
db2$CW <- NA   # Credibility weighted prediction
db2$CO <- NA   # Collective prediction
for (j in 1:5) {
  idx <- db2$state == j
  Y <- cbind(rep(1, sum(idx)),
             T.jt[idx])
  db2$SA[idx] <- Y %*% Bj[,j]
  db2$CW[idx] <- Y %*% CW(j)
  db2$CO[idx] <- Y %*% B.gls
}
rm(j, idx, Y)
```

```{r}
#| echo: true
#| label: fig-credibility-estimates
#| fig-cap: "Credibility estimates for Hachemeister data. The green colored line corresponds to the collective estimate.  The light purple line is the stand-alone estimate for the state and the dark purple line is the credibility weighted estimate."

p <- ggplot(data = db2,
       mapping = aes(x = time,
                     y = severity,
                     group = state)) +
  geom_line(mapping = aes(x = time, y = SA),
            color = "#f1b6da") +
  geom_line(mapping = aes(x = time, y = CW),
            color = "#d01c8b") +
  geom_line(mapping = aes(x = time, y = CO),
            color = "#4dac26") +
  labs(x = "Time (in Qs)",
       y = "Severity") +
  scale_x_continuous(breaks = (1:6) * 2,
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(1204.51, 2809.63)) +
  facet_wrap(vars(state), labeller = label_both)
p
```

```{r}
CG <- tapply(W.jt * T.jt, S, sum) / W.jb
round(CG, 3)
```
and notice that they are all close to each other.
The largest difference between any two states is 
`r round(max(outer(CG, CG, function(x,y) abs(x - y))), 3)`.

```{r}
#| include: true

j0 <- sum(W.jb * CG) / W.bb
```

```{r}
#| include: true

sg <- sig.sq(X.jt, T.jt - j0, W.jt, db$state)$sigma.sq
D <- tau(sg, X.jt, T.jt, W.jt, db$state)$D
CW.one.center <- HBG(sg, D, X.jt, T.jt - j0, W.jt, db$state, use.B.gls = TRUE)

rm(sg, D)
```

```{r}
#| echo: true
#| label: tbl-credibility-estimates-one-center-of-gravity
#| tbl-cap: "Credibility matrices and estimated stand-alone, credibility, and collective intercept and slope for the Hachemeister data when the time variable has been centered at the global center of gravity.  Note that the off-diagonal elements of the credibility matrices are nearly zero. For standalone, credibility, and collective estimates the intercept is listed first and the slope second."

kbl(CW.one.center$tb,
    digits = c(0, 4, 4, 2, 2, 2),
    row.names = FALSE,
    col.names = c("State", "Col.1", "Col.2", "Standalone",
                  "Credibility", "Collective"),
    align = "crrrrr",
    format.args = list(big.mark = ','),
    booktabs = TRUE,
    linesep = "") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" " = 1, "Credibility Matrix" = 2, " " = 3))

rm(CW.one.center)
```

```{r}
#| include: true

j0 <- rep(CG, each = 12)
sg <- sig.sq(X.jt, T.jt - j0, W.jt, db$state)$sigma.sq
D <- tau(sg, X.jt, T.jt, W.jt, db$state)$D
CW.many.centers <- HBG(sg, D, X.jt, T.jt - j0, W.jt, db$state, use.B.gls = TRUE)

rm(j0, sg, D)
```

```{r}
#| echo: true
#| label: tbl-credibility-estimates-many-centers-of-gravity
#| tbl-cap: "Credibility matrices and estimated stand-alone, credibility, and collective intercept and slope for the Hachemeister data when the time variable for each state has been centered at its own center of gravity.  Note that the off-diagonal elements of the credibility matrices are exactly zero. For standalone, credibility, and collective estimates the intercept is listed first and the slope second."
kbl(CW.many.centers$tb,
    digits = c(0, 4, 4, 2, 2, 2),
    row.names = FALSE,
    col.names = c("State", "Col.1", "Col.2", "Standalone",
                  "Credibility", "Collective"),
    align = "crrrrr",
    format.args = list(big.mark = ','),
    booktabs = TRUE,
    linesep = "") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" " = 1, "Credibility Matrix" = 2, " " = 3))
```

```{r}
#| include: true

Y <- matrix(c(1,1,1,12), nrow = 2, ncol = 2)
mu.st <- Y %*% reduce(CW.many.centers$B, cbind)
mu.cw <- Y %*% reduce(CW.many.centers$CW, cbind)
mu.co <- Y %*% CW.many.centers$B.col
tb <- tibble(state = rep(1:5, each = 2),
             time = rep(c(1, 12), 5),
             sev.st = as.vector(mu.st),
             sev.cw = as.vector(mu.cw),
             sev.co = rep(as.vector(mu.co), 5))
tc <- tibble(state = 1:5,
             time = CG)

rm(Y, mu.st, mu.cw, mu.co, CG)
```

```{r}
#| echo: true
#| label: fig-credibility-estimates-centers-of-gravity
#| fig-cap: "Credibility estimates for Hachemeister's data with time translation to the center of gravity for each state. Each state center of gravity is shown as gray vertical line. Note that all the credibility weighted intercepts (at the center of gravity) and slopes (dark purple) are now strictly between the stand-alone estimates (light purple) and the collective estimates (dark green)."

ggplot(data = tb,
       mapping = aes(x = time,
                     group = state)) +
  geom_vline(data = tc,
             mapping = aes(xintercept = time,
                           group = state),
             color = "gray") +
  geom_line(mapping = aes(y = sev.st),
            color = "#f1b6da") +
  geom_line(mapping = aes(y = sev.cw),
            color = "#d01c8b") +
  geom_line(mapping = aes(y = sev.co),
            color = "#4dac26") +
  scale_x_continuous(breaks = seq(2, 12, by = 2),
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(1204.51, 2809.63)) +
  labs(x = "Time (in Qs)",
       y = "Severity") +
  facet_wrap(vars(state), labeller = "label_both")

rm(tb, tc)
```

